Mass and occupation fraction of dark matter halos hosting Lyman-$\alpha$ emitters at $z\sim 3$

### 2013-11-20 paper/ms.tex
continue editing of the results section

Figure \ref{fig:restriction_mock_and_f_occ_corr} we present the preferred
models in the planes $M_{\rm min}$-$M_{\rm  max}$ and $M_{\rm min}$-$f_{\rm occ}$
both for the comparisons against \cite{Hayashino2004} and
\cite{Ouchi2010}. To make this selection we consider that
a model is consistent with observations if there is a $1$-$\sigma$
overlap between both the correlation length $\theta_0$ and the power
$\beta$. We clearly see from this Figure that the conditions imposed
by \cite{Hayashino2004} are the tightest. Comparing this Figure with
the results shown in Figure \ref{fig:restriction_mock} we see that
practically all models with $M_{\rm max}>10^{12}$ are removed. On the
other hand the comparison against \cite{Ouchi2010} does not
substantially reduce the number of models.

At this point we take the most strict decision to keep 
models consistent with both observational constraints. This
reduces the selection to the models already restricted by
the data in \cite{Hayashino2004} as presented in the lower panels of Figure
\ref{fig:restriction_mock_and_f_occ_corr}. Our main conclusions after
this comparison is that clustering information is able to put
meaningful constraints on the values of $M_{\rm max}$. However, the
possible values for the occupation fraction, despite having a strong correlation
with $M_{\rm min}$, still are in the initial range $0.1\leq f_{\rm
  occ}\leq 1$.

@@

\begin{table}
\begin{center}
\begin{tabular}{cccc}\hline\hline
$\log_{10}M_{\rm min}$ & $\log_{10}M_{\rm max}$ & $f_{\rm occ}$ & $\Delta M$\\\hline
10.4 &10.7 & 0.1\\
 10.5 &10.6 & 0.3\\
 10.5 &10.9 & 0.1\\
 10.5 &11.0 & 0.1\\
 10.6 &10.8 & 0.2\\
 10.6 &11.2 & 0.1\\
 10.6 &11.3 & 0.1\\
 10.6 &11.4 & 0.1\\
 10.6 &11.5 & 0.1\\
 10.6 &11.6 & 0.1\\
 10.6 &11.7 & 0.1\\
 10.7 &11.0 & 0.2\\
 10.8 &11.2 & 0.2\\
 10.8 &11.3 & 0.2\\
 10.8 &11.4 & 0.2\\
 10.9 &11.3 & 0.3\\
 10.9 &11.7 & 0.2\\
 10.9 &11.8 & 0.2\\
 10.9 &11.9 & 0.2\\
 10.9 &12.0 & 0.2\\
 10.9 &12.1 & 0.2\\
 10.9 &12.2 & 0.2\\
 10.9 &12.3 & 0.2\\
 10.9 &12.6 & 0.2\\
 10.9 &12.8 & 0.2\\\hline
\end{tabular}
\end{center}
\caption{\label{table:firstfamily}List of parameters for the first
  family of models. Narrow mass range $\Delta M\leq 1.0$ dex and low
  occupation fraction $f_{\rm occ}\leq 0.3$.} 
\end{table}

\begin{table}
\begin{center}
\begin{tabular}{cccc}\hline\hline
$\log_{10}M_{\rm min}$ & $\log_{10}M_{\rm max}$ & $f_{\rm occ}$ & $\Delta M$\\\hline
10.6 &10.700 & 0.4\\
 10.7 &10.8 & 0.5\\
 10.8 &10.9 & 0.6\\
 10.8 &11.0 & 0.4\\
 10.9 &11.0 & 0.8\\
 10.9 &11.0 & 0.9\\
 10.9 &11.1 & 0.5\\
 11.0 &11.1 & 1.0\\
 11.0 &11.2 & 0.6\\
 11.0 &11.4 & 0.4\\
 11.1 &11.3 & 0.7\\
 11.1 &11.3 & 0.8\\
 11.1 &11.4 & 0.6\\
 11.2 &11.4 & 0.9\\
 11.2 &11.4 & 1.0\\\hline
\end{tabular}
\end{center}
\caption{\label{table:secondfamily}List of parameters for the second
  family of models. Narrow mass range $\Delta M\leq 1.0$ dex and high occupation fraction $f_{\rm occ}>0.3$.}
\end{table}

>>>>

Figure \ref{fig:restriction_mock_and_f_occ_corr} presents the selected models
models in the planes $M_{\rm min}$-$M_{\rm  max}$ and $M_{\rm
  min}$-$f_{\rm occ}$. To make this selection we consider that
a model is consistent with observations if there is a $1$-$\sigma$
overlap between both the correlation length $\theta_0$ and the power
$\beta$. Comparing this Figure
\ref{fig:restriction_mock_and_f_occ_corr} with the results shown in Figure
\ref{fig:restriction_mock} we see that the new constraint disfavors
practically all models with $M_{\rm max}>10^{12}$.

Our main conclusions after this comparison is that clustering
information is able to put meaningful constraints on the values of
$M_{\rm max}$. However, the possible values for the occupation
fraction, despite having a strong correlation with $M_{\rm min}$
remain unconstrained.

@@

\begin{table}
\begin{center}
\begin{tabular}{cccc}\hline\hline
$\log_{10}M_{\rm min}$ & $\log_{10}M_{\rm max}$ & $f_{\rm occ}$ & $\Delta M$\\\hline
 10.4 &10.7 & 0.1& 0.3 \\
 10.5 &10.9 & 0.1& 0.4 \\
 10.5 &11.0 & 0.1& 0.5 \\
 10.6 &10.8 & 0.2& 0.2 \\
 10.6 &11.2 & 0.1& 0.6 \\
 10.6 &11.3 & 0.1& 0.7 \\
 10.6 &11.4 & 0.1& 0.8 \\
 10.6 &11.5 & 0.1& 0.9 \\
 10.6 &11.6 & 0.1& 1 \\
 10.6 &11.7 & 0.1& 1.1 \\
 10.7 &11.0 & 0.2& 0.3 \\
 10.8 &11.2 & 0.2& 0.4 \\
 10.8 &11.3 & 0.2& 0.5 \\
 10.8 &11.4 & 0.2& 0.6 \\
 10.9 &11.7 & 0.2& 0.8 \\
 10.9 &11.8 & 0.2& 0.9 \\
 10.9 &11.9 & 0.2& 1 \\
 10.9 &12.0 & 0.2& 1.1 \\
 10.9 &12.1 & 0.2& 1.2 \\
 10.9 &12.2 & 0.2& 1.3 \\
 10.9 &12.3 & 0.2& 1.4 \\
 10.9 &12.6 & 0.2& 1.7 \\
 10.9 &12.8 & 0.2& 1.9 \\\hline
\end{tabular}
\end{center}
\caption{\label{table:firstfamily}List of parameters for the first
  family of models. Narrow mass range $\Delta M\leq 1.0$ dex and low
  occupation fraction $f_{\rm occ}\leq 0.3$.} 
\end{table}

\begin{table}
\begin{center}
\begin{tabular}{cccc}\hline\hline
$\log_{10}M_{\rm min}$ & $\log_{10}M_{\rm max}$ & $f_{\rm occ}$ & $\Delta M$\\\hline
 10.5 &10.6 & 0.3 & 0.1 \\
 10.6 &10.7 & 0.4 & 0.1 \\
 10.7 &10.8 & 0.5 & 0.1 \\
 10.8 &10.9 & 0.6 & 0.1 \\
 10.8 &11.0 & 0.4 & 0.2 \\
 10.9 &11.0 & 0.8 & 0.1 \\
 10.9 &11.0 & 0.9 & 0.1 \\
 10.9 &11.1 & 0.5 & 0.2 \\
 10.9 &11.3 & 0.3 & 0.4 \\
 11.0 &11.1 & 1.0 & 0.1 \\
 11.0 &11.2 & 0.6 & 0.2 \\
 11.0 &11.4 & 0.4 & 0.4 \\
 11.1 &11.3 & 0.7 & 0.2 \\
 11.1 &11.3 & 0.8 & 0.2 \\
 11.1 &11.4 & 0.6 & 0.3 \\
 11.2 &11.4 & 0.9 & 0.2 \\
 11.2 &11.4 & 1.0 & 0.2 \\\hline
\end{tabular}
\end{center}
\caption{\label{table:secondfamily}List of parameters for the second
  family of models. Narrow mass range $\Delta M\leq 0.4 $ dex and high occupation fraction $f_{\rm occ}>0.2$.}
\end{table}
